Home Nighttime Cough Monitoring

### 2025-02-26 Lilah Melzer/cough_monitor_analysis.qmd
finally finished CFQR and HC survey scoring

        sum(is.na(c(phys1, phys2, phys3, phys4, phys5, phys14, phys15, phys16))) <= 4,

@@

        sum(is.na(c(emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14))) <= 4,
        (mean(c(emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14)) - 1)

@@

        sum(is.na(c(social20, social21, social22, social23, social24, social25, social26))) <= 3,
        (mean(c(social20, social21, social22, social23, social24, social25, social26)) - 1)

@@

@@

        sum(is.na(c(social22, social23, social27, social28, social29, social30))) <= 3,
        (mean(c(social22, social23, social27, social28, social29, social30)) - 1)

@@

@@

surveys <- full_join(cfqr_parent_6_13, cfqr_children_6_11)
surveys <- full_join(surveys, cfqr_teens_adults)

@@

cfqr_parent_6_13$sid <- as.numeric(cfqr_parent_6_13$sid)
cfqr_children_6_11$sid <- as.numeric(cfqr_children_6_11$sid)
cfqr_teens_adults$sid <- as.numeric(cfqr_teens_adults$sid)
agg_counts <- full_join(agg_counts, cfqr_parent_6_13)
agg_counts <- full_join(agg_counts, cfqr_children_6_11)
agg_counts <- full_join(agg_counts, cfqr_teens_adults)

>>>>

        sum(is.na(c(
          phys1, phys2, phys3, phys4, phys5, phys14, phys15, phys16
        ))) <= 4,

@@

        sum(is.na(c(
          emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14
        ))) <= 4,
        (mean(c(
          emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14
        )) - 1)

@@

        sum(is.na(c(
          social20, social21, social22, social23, social24, social25, social26
        ))) <= 3,
        (mean(c(
          social20, social21, social22, social23, social24, social25, social26
        )) - 1)

@@

# Children aged 12 to 13
cfqr_children_12_13_names <- list(
  "cfq_r_o1" = "phys1", "cfq_r_o2" = "phys2", "cfq_r_o3" = "phys3",
  "cfq_r_o4" = "phys4", "cfq_r_o5" = "phys5", "cfq_r_o6" = "phys6",
  "cfq_r_o7" = "emot7", "cfq_r_o8" = "emot8", "cfq_r_or9" = "emot9",
  "cfq_r_o10" = "emot10", "cfq_r_o11" = "emot11", "cfq_r_o12" = "emot12",
  "cfq_r_o13" = "emot13", "cfq_r_o14" = "emot14", "cfq_r_o15" = "eat15",
  "cfq_r_o16" = "treat16", "cfq_r_o17" = "eat17", "cfq_r_o18" = "treat18",
  "cfq_r_o19" = "eat19", "cfq_r_o20" = "social20", "cfq_r_o21" = "social21",
  "cfq_r_o22" = "social22", "cfq_r_o23" = "social23", "cfq_r_o24" = "social24",
  "cfq_r_o25" = "social25", "cfq_r_o26" = "social26", "cfq_r_o27" = "body27",
  "cfq_r_o28" = "body28", "cfq_r_o29" = "body29", "cfq_r_o30" = "treat30",
  "cfq_r_o31" = "resp31", "cfq_r_o32" = "resp32", "cfq_r_o33" = "resp33",
  "cfq_r_o34" = "resp34", "cfq_r_o35" = "digest35"
cfqr_children_12_13_names <-
  setNames(names(cfqr_children_12_13_names), cfqr_children_12_13_names)
cfqr_children_12_13_reverse <- c(
cfqr_children_12_13 <- df %>%
    cfqr_children_ages_1213_timestamp, cfq_r_o1:cfq_r_o35
    Date = as.Date(cfqr_children_ages_1213_timestamp),
    across(cfq_r_o1:cfq_r_o35, ~ as.numeric(.x))
  rename(all_of(unlist(cfqr_children_12_13_names))) %>%
  mutate(across(all_of(cfqr_children_12_13_reverse), ~ 5 - .x)) %>%
        sum(is.na(c(
          emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14
        ))) <= 4,
        (mean(c(
          emot7, emot8, emot9, emot10, emot11, emot12, emot13, emot14
        )) - 1)
        sum(is.na(c(
          social20, social21, social22, social23, social24, social25, social26
        ))) <= 3,
        (mean(c(
          social20, social21, social22, social23, social24, social25, social26
        )) - 1)
    Survey = "CFQ-R Children Ages 12-13"

@@

        sum(is.na(c(
          social22, social23, social27, social28, social29, social30
        ))) <= 3,
        (mean(c(
          social22, social23, social27, social28, social29, social30
        )) - 1)

@@

# Controls
hc_surveys <- df %>%
    sid, date_v1_cf, date_v1_hc, hc_pediatric_cough_survey_timestamp, q1:q5
    Date = as.Date(hc_pediatric_cough_survey_timestamp),
    Survey = "HC Cough Survey"
    sid, Survey, Date, q1:q5
  filter(!if_all(q1:q5, ~ is.na(.)))
hc_surveys$sid <- as.numeric(hc_surveys$sid)

@@

cf_surveys <- full_join(cfqr_parent_6_13, cfqr_children_6_11)
cf_surveys <- full_join(cf_surveys, cfqr_children_12_13)
cf_surveys <- full_join(cf_surveys, cfqr_teens_adults)
cf_surveys$sid <- as.numeric(cf_surveys$sid)

@@

agg_counts <- full_join(agg_counts, cf_surveys, by = join_by(sid, Date))
agg_counts <- full_join(agg_counts, hc_surveys, by = join_by(sid, Date, Survey))
